# Precheck

Make sure to use a full `polities.csv` file (if you re-run using the output the multiple imputation loop will run into bugs when it comes across NGAs with only one polity)

NB: Using shortened variables.csv file that only uses variables of interest to save computational time. If using full file, may need to renumber variables in Aggr.MI

**Don't rerun this section unless it's a new scrape**
  

# Checks Soc Complx data from exportdat.csv for error

The variable `polities` was used all over the code. MM changed the variable name to `polities_pre` for pre-checked, pre-tidied version in order to distinguish it with the one used for analysis. 

```{r}
polities_raw <- read_csv("inpput/polities.csv")
```

### Quick look at the raw data

```{r polities-quick-plot}
polities_raw %>% 
  transform(Complexity  = factor(Complexity, levels = c("Early", "Medium", "Late"))) %>% 
  ggplot(aes(x = NGA, ymin = Start, y = (Start + End) / 2, ymax = End, colour = Complexity)) +
  geom_errorbar(width = 0.3) +
  geom_text(aes(label = PolName, size = abs(End - Start)), colour = "Black", vjust = -0.1, show.legend = FALSE) + # angle = 90
  scale_size_continuous(range = c(0, 3)) +
  scale_colour_viridis_d() +
  coord_flip()

```

### delete duplicated entries 

Not sure why Dupl is deleted.

```{r}


polities_pre <- polities_raw %>% 
  filter(Dupl == "n")
```

### Vars


`Vars` is a 225 row variables of complexity suchas population, professional soldiers etc.

```{r}
Vars_old <- as.matrix(read.csv('input/variables.csv', header=TRUE))

Vars <- read_csv("input/variables.csv") %>% # originally as.matrix()
  mutate(Variable = paste(Subsection, Variable)) # Creating unique variable/section combinations
# Vars[,1] <- paste(Vars[,2],Vars[,1]) 
```


## dat

`dat` seems to be a matrix that contain nearly 40k entries of changes in social complexity on variables such as ...wakaran! 
Not sure why matrix is used for `dat`. Trying tibble.
```{r}
# dat_old <- read.table('input/exportdat.csv', sep=",", header=TRUE, quote = "", colClasses = "character")
dat <- 
  read_csv("input/exportdat.csv", col_types = cols(`Value To` = col_double())) %>%  # without col_types, returns parsing failures on row 5342, 18249, 18750.
  filter(Section %in% c("Social Complexity variables",  "Ritual variables", "Religion and Normative Ideology"))  %>%   # Section is set in !MI.R
  mutate(Variable = paste(Subsection, Variable)) # ISSUE: str_c does not work: "a" + NA = NA. 
  
```

### SCdat

At first glance, `SCdat` seems to be a modified `dat` which is generated by filtering its `Variables` by `Vars`'s `Variables`. 
After that, it seems that scdat filters for the Polity that matches with `polities`'s PolID.
Is this correct??


```{r}
Vars %>%  pull(Variable) %>% unique()
# SCdat <-
  dat %>% 
  filter(Variable %in% Vars$Variable) %T>% print(dim(.)) %>%  
  filter(Polity %in% polities$PolID) %T>% print(dim(.))
print(dim(dat))
dat <- SCdat
SCdat <- matrix(nrow = 0, ncol = 0)

# for(i in 1:nrow(polities)) {
#    dt <- dat_tmp[dat_tmp$Polity==polities$PolID[i],]
#    SCdat <- rbind(SCdat,dt)
# }

SCdat <- SCdat[,c(1,2,5,6,7,8,9,10,11,12)]
row.names(SCdat) <- NULL

# Convert categorical values to numbers. Ignore warnings: they will be taken care off in the next step -- in errors
for(i in 1:nrow(SCdat)){
   for(j in 4:5){
       if(SCdat[i,j] == "present"){SCdat[i,j] <- "1"}   
      if(SCdat[i,j] == "inferred present"){SCdat[i,j] <- "0.9"}   
      if(SCdat[i,j] == "inferred absent"){SCdat[i,j] <- "0.1"}   
      if(SCdat[i,j] == "absent"){SCdat[i,j] <- "0"}   
      if(SCdat[i,j] == "none"){SCdat[i,j] <- "0"}
      if(SCdat[i,j] == "daily"){SCdat[i,j] <- "6"}   
      if(SCdat[i,j] == "weekly"){SCdat[i,j] <- "5"}
      if(SCdat[i,j] == "monthly"){SCdat[i,j] <- "4"}  
      if(SCdat[i,j] == "seasonally"){SCdat[i,j] <- "3"}  
      if(SCdat[i,j] == "yearly"){SCdat[i,j] <- "2"}   
      if(SCdat[i,j] == "once per generation"){SCdat[i,j] <- "1"}   
      if(SCdat[i,j] == "once in a lifetime"){SCdat[i,j] <- "0"}    
      if(SCdat[i,j] == "whole polity"){SCdat[i,j] <- "3"}      
      if(SCdat[i,j] == "majority"){SCdat[i,j] <- "2"}      
      if(SCdat[i,j] == "substantial minority"){SCdat[i,j] <- "1"}      
      if(SCdat[i,j] == "elites"){SCdat[i,j] <- "0"}          
      if(SCdat[i,j] == "inactive"){SCdat[i,j] <- "1"}
      if(SCdat[i,j] == "active"){SCdat[i,j] <- "2"}          
      if(SCdat[i,j] == "moralizing"){SCdat[i,j] <- "3"}          
      if(SCdat[i,j] == "monotheistic"){SCdat[i,j] <- "1"}     
      if(SCdat[i,j] == "polytheistic"){SCdat[i,j] <- "2"}                                                     
      if(SCdat[i,j] == "not applicable"){SCdat[i,j] <- "unknown"}      
      if(SCdat[i,j] == "suspected unknown"){SCdat[i,j] <- "unknown"}      
      if(SCdat[i,j] == "unknown"){SCdat[i,j] <- NA}     
   }}
SCdat <- SCdat[is.na(SCdat[,4])==FALSE,]
dat <- SCdat
for(i in 1:nrow(SCdat)){
   dat[i,4] <- as.numeric(SCdat[i,4])
}
errors <- SCdat[is.na(dat[,4]),]

SCdat <- SCdat[is.na(dat[,4])==FALSE,]
dat <- SCdat[SCdat[,5]!="",]
datNA <- dat
for(i in 1:nrow(dat)){
   datNA[i,5] <- as.numeric(dat[i,5])
}
errors <- rbind(errors,dat[is.na(datNA[,5]),])

# Change BCE to negative years and remove CE. 
for(i in 1:nrow(SCdat)){
   if(substr(SCdat[i,6], (nchar(SCdat[i,6]) - 2) , nchar(SCdat[i,6]) ) =="BCE" )
   {a <- -as.numeric(substr(SCdat[i,6], 1, (nchar(SCdat[i,6]) - 3)))
    SCdat[i,6] <- a}
   if(substr(SCdat[i,7], (nchar(SCdat[i,7]) - 2) , nchar(SCdat[i,7]) ) =="BCE" )
   {a <- -as.numeric(substr(SCdat[i,7], 1, (nchar(SCdat[i,7]) - 3)))
    SCdat[i,7] <- a}
}
for(i in 1:nrow(SCdat)){
   if(substr(SCdat[i,6], (nchar(SCdat[i,6]) - 1) , nchar(SCdat[i,6]) ) =="CE" )
   {a <- as.numeric(substr(SCdat[i,6], 1, (nchar(SCdat[i,6]) - 2)))
    SCdat[i,6] <- a}
   if(substr(SCdat[i,7], (nchar(SCdat[i,7]) - 1) , nchar(SCdat[i,7]) ) =="CE" )
   {a <- as.numeric(substr(SCdat[i,7], 1, (nchar(SCdat[i,7]) - 2)))
    SCdat[i,7] <- a}
}

dat <- SCdat[SCdat[,6]!="",]
for(i in 1:nrow(dat)){
   dat[i,6] <- as.numeric(dat[i,6])
}
errors <- rbind(errors,dat[is.na(dat[,6]),])

dat <- SCdat[SCdat[,7]!="",]
for(i in 1:nrow(dat)){
   dat[i,7] <- as.numeric(dat[i,7])
}
errors <- rbind(errors,dat[is.na(dat[,7]),])

write.csv(errors, file="errors.csv",  row.names=FALSE)
write.csv(SCdat, file="SCdat.csv",  row.names=FALSE)

rm(i,j,var,dat,dt,datNA,a,polities,Vars)

## Checks for polity inclusions
#dat <- read.table('exportdat.csv', sep=",", header=TRUE, quote = "", colClasses = "character")
#dat <- dat[dat$Section==Section,]
#polities_wiki <- levels(as.factor(dat$Polity))
#polities <- read.csv('polities.csv', header=TRUE)
#polities <- polities[polities$Dupl=="n",]
#polities <- levels(as.factor(polities$PolName))

#extras <- vector(length=0)
#for (i in 1:length(polities_wiki)){
#   if(any(polities_wiki[i] == polities)==FALSE){extras <- c(extras, polities_wiki[i])}
#}
#missing <- vector(length=0)
#for (i in 1:length(polities)){
#   if(any(polities[i] == polities_wiki)==FALSE){missing <- c(missing, polities[i])}
#}
#write.csv(extras, file="extras.csv",  row.names=FALSE)
#write.csv(missing, file="missing.csv",  row.names=FALSE)








```
