# Inspector


this is an appendix for `02_polities.Rmd` dedicated just for inspecting the produced dataframes and missing values / wrong values.



## Saving Susiana's SyCalUm	uncertainty


## df_min

```{r}
df_disputed_uncertain %>% View() # SyCaalUm available
df %>% filter(NGA == "Susiana") %>%  View() # available
df_min %>% filter(NGA == "Susiana") %>%  View() # available
df_join %>% filter(NGA == "Susiana", PolID == "SyCalUm") %>%  View() # available at t=7000 professional priesthood
df_join%>% filter(NGA == "Susiana", PolID == "SyCalUm") %>%  View() # available at t=700 professional priesthood
df_join2 %>% filter(NGA == "Susiana", PolID == "SyCalUm") %>%  View() # available at t=700 professional priesthood
df_join_shortname %>% filter(NGA == "Susiana", PolID == "SyCalUm") %>%  View() # available at t=700 professional priesthood

df_spread %>% filter(NGA == "Susiana", PolID == "SyCalUm") %>%  View() # yes
df_spread_prop %>% filter(NGA == "Susiana", PolID == "SyCalUm") %>%  View() # yes

aaaaaa

```

## verify 


## Saving Susiana's IrSasn1 LegCode


```{r}
SCdat_df %>% filter(Polity == "IrSasn1") # 201 entries
SCdat_df %>% filter(Polity == "IrSasn1", Variable == "Law Formal legal code") # Kachi, Sogdiana, Susiana, all 0 AND 1, disputed./
df_disputed_uncertain %>% filter(Polity == "IrSasn1") # not available for Susiana, but in sogdiana it is available. law formal leg code 0.
df %>% filter(Polity == "IrSasn1", Variable == "Law Formal legal code") # not available, but in sogdiana it is available. law formal leg code 0
df %>% filter(Polity == "IrSasn1") # Sogdiana, Kachi, Susiana
df %>% filter(NGA == "Sogdiana", Variable == "Law Formal legal code") # 

df_ranged %>% filter(NGA == "Susiana", Polity == "IrSasn1") %>% View() # not available, but in sogdiana it is available. law formal leg cod
df_join %>% filter(NGA == "Susiana", PolID == "IrSasn1") %>% View() # d
df_join %>% filter(NGA == "Susiana", Variable == "Law Formal legal code") %>% View() # d
df_join %>% filter(NGA == "Sogdiana", PolID == "IrSasn1") %>% View() # not available,


output_df %>% filter(NGA =="Susiana", PolID == "IrSasn1") # ground truth
output_df %>% filter(PolID == "IrSasn1") # ground truth. no 
output_df %>% filter(NGA == "Sogdiana") # ground truth. no 
df %>% filter(NGA == "Sogdiana") # ground truth. no 
df_spread_prop %>% filter(NGA =="Susiana", PolID == "IrSasn1")
df_spread_prop %>% filter(PolID == "IrSasn1")


polities_df %>% filter(NGA == "Susiana")
polities_df %>% filter(NGA == "Sogdiana")
```


## Saving Susiana's IrSusa2's PolPop

Now the discrepancy is down to 15 rows from 28 rows.
```{r}
# Find what's different

ground_truth <- output_df %>% filter(PolID == "IrSusa2", Date == -3800) 
bokeh <- df_spread_prop %>% filter(PolID == "IrSusa2", t == -3800) 
a <- ground_truth[, 5:ncol(bokeh)]  %>% as.numeric()
b <- bokeh[, 5:ncol(bokeh)] %>% as.numeric()
xor(is.na(a), is.na(b))

SCdat_df %>% filter(Polity == "IrSusa2", Variable == "Social Scale Polity Population") # no entries for Date -3800!
SCdat %>% as_tibble() %>% filter(Polity == "IrSusa2", Variable == "Social Scale Polity Population") # no entries for Date -3800! where did the value come from then?
output_df %>% select(PolID, PolPop, Date) %>%  filter(PolID == "IrSusa2") # available from -3800, with value 873, and -3700 with roughly 13500 pop
df_spread_prop %>% select(PolID, PolPop, t) %>%  filter(PolID == "IrSusa2") # available from -3700
SCdat_df %>% filter(Polity == "IrSusa2")

polities_df %>% filter(PolName == "IrSusa2")

mioutput_df <- read_csv("output/reproduction/MIoutput.csv")
mioutput_df_original <- read_csv("output/original/MIoutput.csv")

mioutput_df_original %>% filter(PolID == "IrSusa2")

Vars_df
# here, dat is dat from ConstrMI.R, specifying iNGA <- 27 (Susiana).
# dat_df <-
  dat %>% 
  as_tibble() %>% 
  filter(Polity == "IrSusa2")
  
  datSC %>% as_tibble() %>% 
    filter(PolID == "IrSusa2")
```
 
Probably CapPop (`Social Scale Population of the largest settlement`) for t=-3800 is borrowed and copied to PolPop (`Social Scale Polity Population`)?
Turns out the "  # Finally populate 'out' with data tied to a range of dates" section in ConstrMI.R is borrowing the value from IrSusa1's t = -3900. This is caused by IrSusa1's entry has date range of -3900 to -3800. To replicate this behaviour, 



## Saving Deccan InHoysa 1200 CapPop of 125000

```{r}
ground_truth <- output_df %>% filter(PolID == "InHoysa", Date == 1200) 
bokeh <- df_spread_prop %>% filter(PolID == "InHoysa", t == 1200) 
a <- ground_truth[, 5:56]  %>% as.numeric()
b <- bokeh[, 5:56] %>% as.numeric()
xor(is.na(a), is.na(b)) # seems like CapPop


SCdat_df %>% filter(Polity == "InHoysa", Variable == "Social Scale Population of the largest settlement") # 
SCdat %>% as_tibble() %>% filter(Polity == "InHoysa") # CapPop not available
SCdat %>% as_tibble() %>% filter(NGA == "Deccan", Variable == "Social Scale Population of the largest settlement") # InChaKl has Date.From 1150 Value 12500, 50000 for Date1100
polities_df %>% filter(NGA == "Deccan")# InChakl from 974 to 1055, InHoysa from 1192 to 1253. 1192 tsukurou InHoysa
```

Seems that InChaKl lasted 973 to 1191 in Seshat page. In polities_df it's 974 to 1055.

```{r}





output_df %>% select(PolID, PolPop, Date) %>%  filter(PolID == "IrSusa2") # 
df_spread_prop %>% select(PolID, PolPop, t) %>%  filter(PolID == "IrSusa2") # 
SCdat_df %>% filter(Polity == "IrSusa2")

df_centuries_redundant %>% filter(NGA == "Deccan", Variable == "Social Scale Population of the largest settlement")


```