---
title: "Moralizing Gods"
author: ["Minoru Matsui^[Fujitsu Design]"]
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
link-citations: yes
description: "Moralizing Gods paper reproduction"
monofont: "Source Code Pro"
---

# Introduction

Placeholder


## Licence
## Japanese references

<!--chapter:end:index.Rmd-->


# Precheck

Placeholder


### Quick look at the raw data
### delete duplicated entries 
### Vars
## dat filtering it into SCdat
## Recode
## inspect

<!--chapter:end:01_precheck.Rmd-->

# !diagnostics off

# Polities
  
```{r polities}
# !diagnostics off

Vars_df <- read_csv("input/variables.csv")

polities_df <- 
  polities_pre %>% 
  filter(!NGA %in% c("Crete", "Galilee", "Middle Ganga")) %>%  # Remove new NGAs
  filter(!PolID %in% c("IdCJBun", "IdKalin")) %>%  # Remove low-coverage polities causing bugs in C. Java)
  filter(!PolID %in% c("EsHabsb", "USIllinL", "GbEmpir", "InEInCo", "InBritP", "RuYakuL", "UsIroqL")) #Remove post-colonial polities (also see below for removing post-colonial polities from NGAs with only 2 polities)

NGAs <- levels(polities_df$NGA %>% as.factor()) # warnings maaaaay be okay.
```

# Multiple Imputations 

## ConstrMI.R

`ConstrMI.R` : from 30 NGAs in `polities`, select an NGA e.g., NGAs[1] = "Big Island Hawaii", filter SCdat and polities with that NGA, 

modern version:

input:
  - `polities_df`: a tibble of polities from `polities.csv`, minus duplicate minus new NGAs,etc. A simple list of individual polities per row, with PolIdD and its start/end year. 299 x 11
  - `SCdat`: a tibble of social complexity in 19,042 x 10, created with `01_precheck.Rmd`. NGA, Polity, Variable, Value From, Value To, Date From, Date To...
  

First, one value from a normal distribution created from ranged value (denoted by "range" in `Value Note` in `SCdat`) is used as value
Then "disputed" and "uncertain" is dealt by picking one. Why not just use different values as is, embodying uncertainty?..

```{r}

SCdat %>% filter(`Date From` >= 1600)

# a dumb but fast and readble way to mutate...
df_disputed_uncertain<- SCdat %>%
  filter(
         `Value Note` %in% c("disputed", "uncertain")) %>% # includes both disputed and uncertain
  group_by(Polity, Variable, `Date From`, `Date To`)  %>%
  sample_n(1)  # Randomly sample from disputed and uncertain, eliminate extra rows

df_ranged <- SCdat %>%
  filter(`Value Note` == "range") %>%
  mutate(
    `Value From` = pmap(., function (`Value From`, `Value To`, ...) rnorm(n = 1, mean = (`Value From` + `Value To`) / 2, sd = abs(`Value To` - `Value From`) / (2*1.645))
    ) # seems like pmap() is needed. reference: http://yoshidk6.hatenablog.com/entry/2018/08/06/154117
  ) %>% unnest()

df_else <- SCdat %>%
  filter(!`Value Note` %in% c("disputed", "uncertain", "range"))

df <- bind_rows(df_disputed_uncertain, df_ranged, df_else)
df_min <- df %>%
  select(NGA, Polity, Variable, `Value From`, `Date From`, `Date To`) %>%
  rename(PolID = Polity,
         Value = `Value From`,
         Date = `Date From`,
         DateTo = `Date To`) %>%
  ungroup() %>%
  ungroup() %>%
  ungroup() %>%
  ungroup() # 18823 x 6

# OPTION B: seemed cooler, but apparently way slower probably because of if_else
# a <- SCdat %>% 
#   group_by(NGA) %>% 
#   split(.$`Value Note` %in% c("disputed", "uncertain")) %>% 
#   modify_at("TRUE", sample_n, 1) %>% 
#   bind_rows()
#   mutate(`Value From` = if_else(`Value Note` == "range", 
#                                 )pmap(., function (`Value From`, `Value To`, ...) rnorm(n = 1, mean = (`Value From` + `Value To`) / 2, sd = abs(`Value To` - `Value From`) / (2*1.645))),
#                                 .)) # extremely slow...
                                

# OPTION C: `case_when()` extremely slow. took 3min
# df  %>% 
# mutate(
#   value = case_when(
#     `Value Note` == "range" ~ rnorm(1, mean = (`Value From` + `Value To`) / 2, sd = abs(`Value To` - `Value From`) / (2*1.645)), 
#     TRUE ~ `Value From` # Catch all statement, equivalent to `Value Note` != "range"
#   )
# ) %>% View()

```

# construct output

Join everything together. 

input:

- `df_min`: actual values of polities' social complexity variables.
- `polities_df`: to retrieve the range of years the polities were there.
- 

```{r}

df_join <-  
  inner_join(
    df_min, 
    polities_df,
    by = c("NGA", "PolID")
  ) %>%  # 18,823 x 15. drop NGA because polities_df has only one NGA for a PolID, whilst some PolIDs such as AfGrBct extend to other NGAs, hence produces many NA rows.
  group_by(PolID) %>% 
  mutate(
    PolStartC = (min(Start) / 100) %>% ceiling(), # previously `tmin`. the first century the polity has already started. e.g., if 99CE, 1. 100CE, 1. 101CE, 2.
    PolEndC = (max(End) / 100) %>% floor() # previously `tmmax`. the century the polity ended.
  ) %>% 
  mutate(centuries = map2(PolStartC, PolEndC, seq)) %>% 
  unnest() %>% 
  mutate(
    t = centuries * 100,
    PolStart = PolStartC * 100,
    PolEnd = PolEndC * 100
  ) %>% # convert centuries back to years
  select(-(World.Region:centuries)) %>% # tidying columns
  ungroup() %>% # ungroup before filtering
  filter(Start <= t & End >= t) %>% 
  filter((is.na(DateTo) && !is.na(Date) && (round(Date, -2) == t)) | (!is.na(Date) && !is.na(DateTo) && between(t, Date, DateTo)) | is.na(Date))# filter our if t is not close to Date, for single date datapoints, OR(|, do not use ||)　filter out if t is out of Date-DateTo range, for ranged date datapoints
# df_join 36,982 x 12

```


## inspect

```{r}
df_inspect <- df_join %>% 
  filter(NGA == "Sogdiana", Variable == "Bureaucracy characteristics Full-time bureaucrats")
df_inspect2 <- df_join %>% 
  filter(NGA == "Deccan")

output %>%  as_tibble() %>%  
  filter(NGA == "Sogdiana") %>% View()
]

df_inspect %>% 
  ggplot(aes(x = t, y = Value, colour = PolID)) +
  geom_point() +
  geom_line()
```

# construct output

social complexity variable names in `df_join` (`df_join$Variables`) are joined name of subsection and variable in `Vars_df`.

```{r}

# 
Vars_df_minimum <- 
  Vars_df %>% 
  mutate(Variable = paste(Subsection, Variable)) %>% 
  select(Variable, ShortName)
```


now join them together 

```{r}
df_join_shortname <-
  left_join(df_join, 
            Vars_df_minimum, 
            by = "Variable") %>% 
  mutate(Variable = ShortName,
         ShortName = NULL) # 29191 * 12
```

then `spread()`.

```{r}
unique(df_join_shortname$Variable) %>% length()

df_spread <- 
  df_join_shortname %>% 
  spread(key = Variable, value = Value) %>% 
  mutate(PropCoded = (51 - (select(., AdmLev:WRecord) %>% is.na() %>% rowSums())) / 51
         ) %>% # this isn't working, ISSUE
  arrange(NGA, PolID) # 820 * 77. output's got 817 * 98...

  df_spread  %>% select(AdmLev:WRecord) %>% is.na() %>% rowSums()
```

inspect by table:

```{r}
output_df <- output %>% as_tibble

full_join(output_df %>% select(NGA, PolID, Date), 
          df_spread %>% select(NGA, PolID, t),
          by = c("Date" = "t", "PolID")) %>% View()
```

The `df_spread` got 3 extra rows that aren't available in `output`: IrQajar and TrOttm5 for `t` = 1800 and 1900. ISSUE.


inspect by plot:

```{r fig.height = 20, fig.width = 20}

output_df %>% 
  filter(NGA == "Deccan") %>%
  gather(key = Variable, value = Value, -PolID, -NGA, -Date, -PropCoded) %>% 
  ggplot(aes(x = Date, y = Value, colour = PolID)) +
  geom_point() +
  geom_line() +
  scale_colour_viridis_d() +
  facet_wrap(~Variable, scale = "free_y") 


df_join_short %>% filter(NGA == "Deccan") %>%
  ggplot(aes(x = t, y = Value, colour = PolID)) +
  geom_point() +
  geom_line() +
  scale_colour_viridis_d() +
  facet_wrap(~Variable, scale = "free_y") 
  # theme_tufte()

```



## Aggregate

```{r}

```


```{r}

nrep <- 20
ImpDatRepl <- matrix(NA, nrow=0, ncol=0) 
for(irep in 1:nrep){
  print(irep)
  source("ConstrMI.R")
  source("AggrMI.R")
  source("ImputeMI.R")
  ones <- matrix(data=1,nrow=length(AggrDat[,1]),ncol=1)
  colnames(ones) <- "irep"
  ImpDat <- cbind(AggrDat[,1:4],ImpDat,(ones*irep),AggrDat[,14:32])
  ImpDatRepl <- rbind(ImpDatRepl,ImpDat)
}
```

Remove polity-dates that didn't yield 20 repl and post-colonial polities that couldn't be removed from multiple imputation due to bugs with only 1 polity/NGA

```{r}

polities <- read.csv('polities.csv', header=TRUE)
polities <- polities[polities$PolID != "InGaroL",] # removing here because it caused bugs earlier
write.csv(polities, file="polities.csv",  row.names=FALSE) 
polities <- polities[polities$PolID != "CnHChin",] # removing here because it caused bugs earlier
write.csv(polities, file="polities.csv",  row.names=FALSE) 
polities <- polities[polities$PolID != "PgOrokL",] # removing here because it caused bugs earlier
write.csv(polities, file="polities.csv",  row.names=FALSE) 

ImpDatRepl <- ImpDatRepl[ImpDatRepl$PolID != "InGaroL",] # removing here because it seemed to create bugs when you have only 1 polity in an NGA, so couldn't remove earlier
ImpDatRepl <- ImpDatRepl[ImpDatRepl$PolID != "CnHChin",] # removing here because it seemed to create bugs when you have only 1 polity in an NGA, so couldn't remove earlier
ImpDatRepl <- ImpDatRepl[ImpDatRepl$PolID != "PgOrokL",] # removing here because it seemed to create bugs when you have only 1 polity in an NGA, so couldn't remove earlier

dat_temp <- ImpDatRepl
for(i in 1:nrow(polities)){
  dat <- ImpDatRepl[as.character(ImpDatRepl[,2])==as.character(polities[i,2]),]
  if(nrow(dat)!=0){
    Time <- unique(dat$Time)
    for(j in 1:length(Time)){
      dt <- dat[dat$Time==Time[j],]
      if(nrow(dt) != nrep){
        print(nrow(dt))
        print(dt[1,1:3])
        dat_temp[as.character(dat_temp$PolID)==as.character(dat$PolID[1]) & dat_temp$Time==Time[j],14] <- -99999
      }
    }
  }
}
ImpDatRepl <- dat_temp[dat_temp$irep!=-99999,]

write.csv(ImpDatRepl, file="ImpDatRepl.csv",  row.names=FALSE)
#  end of the new scrape section
```


<!--chapter:end:02_polities.Rmd-->


# Run PCA on ImpDat

Placeholder



<!--chapter:end:03_pca.Rmd-->


# Plot

Placeholder


## Merge PC1_traj.csv with other key info
## FULL MODEL
## Creat Fig. 1 map using manually created map.csv file

<!--chapter:end:04_plot.Rmd-->


# Introduction

Placeholder


## Licence
## Merge PC1_traj.csv with other key info
## FULL MODEL
## Creat Fig. 1 map using manually created map.csv file

<!--chapter:end:moralizing_gods.Rmd-->

