---
title: "Moralizing Gods"
author: ["Minoru Matsui^[Fujitsu Design]"]
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
link-citations: yes
description: "Moralizing Gods paper reproduction"
monofont: "Source Code Pro"
---

# Introduction

The following code was used for analyses in Whitehouse, Francois, Savage..., Turchin (2019), Nature, "Complex societies precede moralizing gods throughout world history", with an "exportdat.csv" file scraped from the Seshat database on 19 Jan 2018.

This software was developed by Peter Turchin and Patrick Savage (Copyright 29 Jan 2018). For the general methodology underlying these analyses please refer to: 
Turchin, P. et al. Quantitative historical analysis uncovers a single dimension of complexity that structures global variation in human social organization. Proc. Natl. Acad. Sci. U. S. A. 115, E144-E151 (2018).
Turchin, P. Fitting dynamical regression models to Seshat data. Cliodynamics 9, (2018).  


## Licence

CC By-NC SA License

Copyright (c) 2018 Peter Turchin and Patrick E. Savage

Permission is hereby granted, free of charge, to any person obtaining a copy of this software and associated documentation files (the "Software"), to deal in the Software under the conditions of Creative Commons Attribution Non-Commercial (CC By-NC SA) licensing (https://creativecommons.org/licenses/by-nc-sa/4.0/legalcode), subject to the following conditions:

Please include the following text in any publication using this software:

This research employed data from the Seshat Databank (seshatdatabank.info) under Creative Commons Attribution Non-Commercial (CC By-NC SA) licensing (https://creativecommons.org/licenses/by-nc-sa/4.0/legalcode).

and cite:

> 1) Whitehouse, Francois, Savage,...,Turchin, "Complex societies and doctrinal rituals precede moralizing gods throughout world history" (2019) Nature.

> 2) Turchin, P. et al. Quantitative historical analysis uncovers a single dimension of complexity that structures global variation in human social organization. Proc. Natl. Acad. Sci. U. S. A. 115, E144-E151 (2018).

> 3) Turchin, P. Fitting dynamical regression models to Seshat data. Cliodynamics 9, (2018).

> 4) Turchin P. et al. 2015. Seshat: The Global History Databank. Cliodynamics 6(1):77窶?107. 

The views and conclusions contained in this document are those of the authors and should not be interpreted as representing the official positions, either expressed or implied, of the Seshat Databank, its collaborative scholarly community, or the Evolution Institute.

The above copyright notice and this permission notice shall be included in all copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.

# Library

The following packages must be installed

```{r install-packages}
# install.packages("maps", repos = "http://cran.us.r-project.org")
# install.packages("plotrix", repos = "http://cran.us.r-project.org")
# install.packages("plyr", repos = "http://cran.us.r-project.org")

```

...then loaded

```{r}
library(maps)
library(plotrix)
# library(plyr) # But maybe shouldn't load this when loading dplyr for confirmatory analyses)
library(tidyverse)
library(magrittr)
library(ggthemes)

```
## Japanese references

[kohske](https://rpubs.com/kohske/479704)
