---
title: "Moralizing Gods"
author: ["Minoru Matsui^[Fujitsu Design]"]
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
link-citations: yes
description: "Moralizing Gods paper reproduction"
monofont: "Source Code Pro"
---

# Introduction

Placeholder


## Licence

<!--chapter:end:index.Rmd-->

# Precheck

Make sure to use a full `polities.csv` file (if you re-run using the output the multiple imputation loop will run into bugs when it comes across NGAs with only one polity)

NB: Using shortened variables.csv file that only uses variables of interest to save computational time. If using full file, may need to renumber variables in Aggr.MI

**Don't rerun this section unless it's a new scrape**
  
  
```{r}
# setwd("/Users/pesavage/Documents/Research/Oxford Seshat/Data/MoralizingGods")
Section1 <- "Social Complexity variables"
Section2 <- "Ritual variables"
Section3 <- "Religion and Normative Ideology"
source("precheck.R")
```

<!--chapter:end:01_precheck.Rmd-->


# Polities

Placeholder



<!--chapter:end:02_polities.Rmd-->


# Run PCA on ImpDat

Placeholder



<!--chapter:end:03_pca.Rmd-->

# Plot

Graphs PCA results for Figure 3 of the PCA article. (see Figure3.R for more code) 
and for the Suppl Materials: all regions


```{r plot}

# setwd("C:/Users/Peter Turchin/Google Drive/2.Seshat/1.R/PCA-MI")
dat <- read.table("PC1_traj.csv", sep=",", header=TRUE)
NGAs <- c("Upper Egypt","Middle Yellow River Valley")

colors <- c("red","blue","darkgreen","brown","tan","black","orange","cyan","darkgrey")
colors <- c(colors,colors,colors)
shade_colors <- c("pink","lightblue","lightgreen","tan")
x_ends <- c(-5000,2000)
y_ends <- c(0,1)
plot(x_ends, y_ends, "n", xlim = x_ends, ylim=y_ends, xlab="year", ylab="PC1", main = "")
legend("topleft", NGAs, lty=1, lwd=3, bty="n", col=colors)

for(j in 1:length(NGAs)){
  NGA <- NGAs[j]
  gdat <- dat[dat[,1]==NGA,]
  polygon(x=c(gdat[,3],rev(gdat[,3])),y=c(gdat$Upper,rev(gdat$Lower)), col=shade_colors[j], border=NA)
  lines(gdat[,3],gdat$Mean, lwd=3, col=colors[j])
  lines(gdat[,3],gdat[,5], lwd=1, lty = 2, col=colors[j])
  lines(gdat[,3],gdat[,6], lwd=1, lty = 2, col=colors[j])
  text(x=x_ends[1], y=(y_ends[2] - .5*j), NGA, col=colors[j], pos=4)
}

```

## Merge PC1_traj.csv with other key info


```{r}

dat <- read.table("PC1_traj.csv", sep=",", header=TRUE)
dat2 <- read.table("polities.csv", sep=",", header=TRUE)
dat <- merge(dat,dat2,by="PolID")
dat2 <- read.table("NGAcoords.csv", sep=",", header=TRUE)
dat <- merge(dat,dat2,by.x="NGA.y",by.y="NGA")
library(plyr)
dat<-rename(dat, c("NGA.y" = "NGA"))
dat<-rename(dat, c("NGA.x" = "OriginalNGA"))
dat<-dat[order(dat$NGA, dat$Time),]
dat<-subset(dat,dat$Time>=dat$Start & dat$Time<=dat$End)
write.csv(dat, file="PC1_traj_merged.csv",  row.names=FALSE)
```


# Run pre-/post-moralizing gods analyses

```{r}
source("BigGodAnalysesEditedV2.R")

```



# Run logistic regression

```{r}
source("RegrDat.R")

```


## FULL MODEL

```{r}
RD1 <- RegrDat[is.na(RegrDat$Lag1) == FALSE,]
RD2 <- RD1[is.na(RD1$Lag2) == FALSE,]
LogistRegrDat = as.data.frame(cbind(RD2$MG,RD2[,c(36,51:54)]))
source("LogistRegr.R")
```




## Creat Fig. 1 map using manually created map.csv file

```{r}
source("Seshat_BG_map.r")

```



<!--chapter:end:04_plot.Rmd-->

